Constant-round Blind Classical Verification of Quantum Sampling

### 2020-07-26 qpip0.tex
Redo z_ideal proof for parallelrep

Now let $z_{true}$, as a mixed state, be correctly sampled from the $\SampBQP$ instance $D_x$,
and let $z_{ideal, i}=\tr(z_{good, i})z_{true}$.
We show that $z_{ideal, i}$ is close to $z_{good, i}$.
\begin{theorem}
	$\tr\abs{z_{good, i}-z_{ideal, i}}\leq O(\varepsilon)$ \Ethan{Check thm statement again later}
\end{theorem}
\begin{proof}

	% \begin{align}
	%     &\vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi} \nn \\
	%     =& \bra{e_i, \psi_{1^{i-1}1,\gamma}} U^\dag P_{acc,i,z} U \ket{e_i\psi_{1^{i-1}1,\gamma}} +\hannote{poly terms?}+ \negl(n)
	% \end{align}

	For every $i\in [m]$ and every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp}, consider the following composite strategy of the prover for the naive $\QPIP_0$ Protocol, Protocol~\ref{proto:qpip0_naive}. Note that the prover only interact with the verifier in Step~\ref{step:urmila-in-naive} of Protocol~\ref{proto:qpip0_naive} where Protocol~\ref{proto:urmila4} is run, so we describe the prover's action in turns of the four rounds of communication in Protocol~\ref{proto:urmila4}.

@@

	Denote the result we would get when $c=1$ by $z_{composite,i}$.

	By property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}, the above strategy is accepted with probability $1-\negl(n)$ when the prover didn't abort. Since the prover's strategy is also efficient, by Lemma~\ref{lem:naive-qpip0-binding},
	\begin{align}
		(d,z_{composite,i})\approx_{c, O(\eps)}(d,z_{ideal,i})
	\end{align}

	\Ethan{Is this particular $z_{ideal, i}$ defined? As in, what's its corresponding accept probability?}

	By construction, when $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$ succeeded, the corresponding output would be $z_{good,i}$. Also note that this is the only case where the verifier won't reject, so $(d,z_{composite,i})=(d,z_{good,i})$, where $(d,z_{good,i})$ is defined as:

	$$\begin{cases}
		(d,z_{good,i}) \la (\Acc, z_{good,i}/|z_{good,i}|) & \text{with probability } |z_{good,i}|\\
						(d,z_{good,i}) = (\Rej,\bot)  & \text{otherwise }
	\end{cases}$$.

	% where  $(d,z)_{good,i} \defeq (\Acc, z_{good,i}) + (1-|z_{good,i}|)(\Rej,\bot)$ \hannote{correct notation? operational def?} .

	Therefore

	\begin{align}
		(d,z_{good,i})\approx_{c, O(\eps)}(d,z_{ideal,i}).
	\end{align}
\end{proof}

>>>>

Now let $z_{true}$, as a mixed state, be correctly sampled from the $\SampBQP$ instance $D_x$,
and let $z_{ideal, i}=\tr(z_{good, i})z_{true}$.
We show that $z_{ideal, i}$ is close to $z_{good, i}$.
\begin{theorem}
	\label{thm:zgood-zideal}
	$\tr\abs{z_{good, i}-z_{ideal, i}}\leq O(\varepsilon)$ \Ethan{Check thm statement again later}
\end{theorem}
\begin{proof}
	For every $i\in [m]$ and every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp}, consider the following composite strategy of the prover for the naive $\QPIP_0$ Protocol, Protocol~\ref{proto:qpip0_naive}. Note that the prover only interact with the verifier in Step~\ref{step:urmila-in-naive} of Protocol~\ref{proto:qpip0_naive} where Protocol~\ref{proto:urmila4} is run, so we describe the prover's action in turns of the four rounds of communication in Protocol~\ref{proto:urmila4}.

@@

	Denote the result we would get when $c=1$ by $z_{composite,i}$. By construction, when $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$ succeeded, the corresponding output would be $z_{good,i}$. Also note that this is the only case where the verifier won't reject, so $z_{composite,i}=z_{good,i}$.

	By property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}, the above strategy is accepted with probability $1-\negl(n)$ when the prover didn't abort. Since the prover's strategy is also efficient, by Lemma~\ref{lem:naive-qpip0-binding},
	$\tr\abs{z_{composite,i}-z_{ideal,i}}=O(\eps)$.
\end{proof}
